Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-28 1607 - JMC for g2/Paper/JMC_dis.tex
Added references

At finite scales, the only way to preserve the validity of the
Burkhardt-Cottingham sum rule is if
%that is derived at the cross section level (under suitable assumptions on the
%high-energy behavior of te hspin-flip amplitude) rather than from an analysis
%of collinear correlators, as done here, 
%to be strictly valid, we obtain a
%strong constraint on the transversity function, 
\begin{align}
   \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
\label{eq:ABsumrule}
\end{align}
Interestingly, one can show that this constraint, if valid at any given scale
$Q_0$ is conserved through QCD evolution. However, we think that this
constrain cannot be satisfied in general, since it is broken in perturbative
QCD~\cite{Kundu:2001pk} and models (see, e.g., \cite{}).

E or explicitly as, \eg, in the quark
target model \cite{Kundu:2001pk} -- i.e., if $g_2$ integrates to a finite but
nonzero number -- 
If we assume that the BC sum rule is broken by a {\em finite} amount, we
obtain that $h_1(x)/x$ must be integrable, implying a 
a bound on the small $x$ behavior of the transversity, 
\begin{align}
  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\label{eq:ABbound}
\end{align}
This bound will be very useful, \eg, in transversity fits, where the data at
small $x$ is, as yet, very limited, and in general for proper extrapolations
when calculating moments.

The first moment is the first in which a contribution from the pure twist-3 part of $g_2$ appears:
\begin{align}
  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
    + \frac{2M_q-m_q}{\Lambda} h_1^q[1] \bigg)
\end{align}
where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the tensor charge. 
The third moment is also interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and interpreted as as the average color force experienced by the struck quark as it exits the nucleon \cite{Burkardt:2012sd}:
\begin{align}
  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
    + \frac{3M_q-m_q}{\Lambda} h_1^q[2] \bigg)
\end{align}
In both cases, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted
\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound \eqref{eq:ABbound} promise to improve future transversity fits. What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator. We will, however, briefly discuss perspectives on how to measure it. Therefore the pure twist-3 part can, in principle, be properly isolated.

>>>>

At finite scales, the only way to preserve the validity of the
Burkhardt-Cottingham sum rule is if
%that is derived at the cross section level (under suitable assumptions on the
%high-energy behavior of te hspin-flip amplitude) rather than from an analysis
%of collinear correlators, as done here, 
%to be strictly valid, we obtain a
%strong constraint on the transversity function, 
\begin{align}
   \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
\label{eq:ABsumrule}
\end{align}
Interestingly, one can show that this constraint, if valid at any given scale
$Q_0$ is conserved through QCD evolution. However, we think that this
constrain cannot be satisfied in general, since it is broken in perturbative
QCD~\cite{Kundu:2001pk} and models (see, e.g., \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}).

If we assume that the BC sum rule is broken by a {\em finite} amount, we
obtain that $h_1(x)/x$ must be integrable, implying a 
a bound on the small $x$ behavior of the transversity, 
\begin{align}
  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\label{eq:ABbound}
\end{align}
This bound can be very useful, \eg, in transversity fits, where the data at
small $x$ is, as yet, very limited, and in general for proper extrapolations
when calculating moments.

The first moment is the first in which a contribution from the pure twist-3 part of $g_2$ appears:
\begin{align}
  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
    + \frac{2M_q-m_q}{\Lambda} h_1^q[1] \bigg)
\end{align}
where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the tensor charge.

The second moment is also interesting because the pure twist-3 part can be
related to quark-gluon-quark correlators, see \cite{Jaffe:1996zw}, and
interpreted as as the average color force experienced by the struck quark as
it exits the nucleon \cite{Burkardt:2012sd}: 
\begin{align}
  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
    + \frac{3M_q-m_q}{\Lambda} h_1^q[2] \bigg)
\end{align}
In both cases, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} or fitted
\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound
\eqref{eq:ABbound} promise to improve future transversity fits. What is less
obvious is how to calculate $M_q-m_q$ from first principles, since this is
related to the spectral function of the quark propagator. We will, however,
briefly discuss perspectives on how to measure it. Therefore the pure twist-3
part can, in principle, be properly isolated. For experimental
measurements of $d_2$, see, e.g., Refs.~\cite{Anthony:2002hy,Slifer:2008xu,Solvignon:2013yun,Posik:2014usi,Flay:2016wie}.
